Periodograms for Multiband Astronomical Time Series

### 2015-02-04 writeup/paper.tex
ZI edits for caption fig. 9

We suggest the following procedure for determining periods in future multiband datasets:
\begin{enumerate}
   \item As a first pass, find a set of candidate frequencies using the multiband periodogram. This is a fast linear optimization that can be trivially parallelized.
   \item Within these candidate frequencies, use the much more costly template-fitting procedure to choose the optimal period from among the handful of candidates.
   \item Compute a goodness-of-fit statistic for the best-fit template to determine whether the fit is suitable; if not, then apply the template-fitting procedure across the full period range.
\end{enumerate}
Here we briefly explore simulated LSST observations of RR Lyrae stars in order to gauge the effectiveness of the first step in this strategy; the effectiveness of the template-fitting step will be explored further in future work.
Rather than doing the full analysis including the final template fits, we will focus on the ability of the multiband periodogram to quickly provide suitable candidate periods under the assumption that the S10 template algorithm will then select or reject the optimial period from this set.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{fig09.pdf}
  \caption{
    Fraction of periods correctly determined for LSST RR Lyrae as a function
    of observing time and $g$-band magnitude, for the multiband (solid lines)
    and single-band supersmoother (dashed lines) approaches.
  } 
  \figlabel{LSST_sims}
\end{figure}

>>>>

We suggest the following procedure for determining periods in future multiband datasets:
\begin{enumerate}
   \item As a first pass, find a set of candidate frequencies using the multiband periodogram. This is a fast linear optimization that can be trivially parallelized.
   \item Within these candidate frequencies, use the much more costly template-fitting procedure to choose the optimal period from among the handful of candidates.
   \item Compute a goodness-of-fit statistic for the best-fit template to determine whether the fit is suitable; if not, then apply the template-fitting procedure across the full period range.
\end{enumerate}
Here we briefly explore simulated LSST observations of RR Lyrae stars in order to gauge the effectiveness of the first step in this strategy; the effectiveness of the template-fitting step will be explored further in future work.
Rather than doing the full analysis including the final template fits, we will focus on the ability of the multiband periodogram to quickly provide suitable candidate periods under the assumption that the S10 template algorithm will then select or reject the optimal period from this set.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{fig09.pdf}
  \caption{
    Fraction of periods correctly determined for LSST RR Lyrae as a function
    of the length of the observing season and the mean $g$-band magnitude, for the multiband (solid lines)
    and single-band supersmoother (dashed lines) approaches.
  } 
  \figlabel{LSST_sims}
\end{figure}
